A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-15 EvoPar2017/paper.Rnw
minor changes

The graph that plots the time to solution of every instance of the
experiment vs. entropy is shown in \ref{fig:entropy}. There is a clear
trend towards experiments with lower entropy taking more time and
experiments with higher entropy taking more time, which indeed can be
statistically fit to a linear model. This dependence on entropy is
much clearer than the assumed dependence on the number of users, which
is represented in the graph by dot color, and even the number of PUTs
or contributions, which is represented by dot size. You can see a
clearly blue and big dot, meaning more than 40 different IPs
participating and around 1500 PUTs in the high end of the graph,
showing that it took the longest to find the solution. On the other
hand, clearly red and small dots are on the lowest end of the graph,
indicating that it took a short time to find the solution as long as
the entropy is high.

@@

Our main intention in this paper was to configure an evolutionary
algorithm in a volunteer computing environment to improve its
efficiency and eventually find out what this efficiency depends
on. The baseline configuration that we had used in other papers  included
{\em overlaps} or volunteers running islands that had actually started in
a previous experiment instance in the set. In previous papers, we were
interested in measuring the number of users or their behavior in bulk
and this overlap was not so important, but
in this case our focus was on the evolutionary algorithm so we had to
make all volunteers in it started more or less at the same time and
from a random population. In fact, we managed to do so, except in some
byzantine cases, by making the clients restart when the cache size
collapses to 1 or to a size much smaller than the current; we called
this client configuration {\tt reboot} and {\tt cachecrash}.  This
configuration achieves a positive secondary effect: all clients
contribute to fill the cache, having thus an actual effect on the
chromosome pool and effectively making all clients present contribute
to the simulation.

>>>>

The graph that plots the time to solution of every instance of the
experiment vs. entropy is shown in \ref{fig:entropy}. There is a clear
trend towards experiments with lower entropy taking more time and
experiments with higher entropy taking more time, which indeed can be
statistically fit to a linear model. This dependence on entropy is
much clearer than the assumed dependence on the number of users, which
is represented in the graph by dot color, and even the number of PUTs
or contributions, which is represented by dot size. You can see a
clearly blue and big dot, meaning more than 40 different IPs
participating and around 1500 PUTs in the high end of the graph,
showing that it took the longest to find the solution. On the other
hand, clearly red and small dots are on the lowest end of the graph,
indicating that it took a short time to find the solution as long as
the entropy was high.

@@

Our main intention in this paper was to configure an evolutionary
algorithm in a volunteer computing environment to improve its
efficiency and eventually find out on what this efficiency depends
on. The baseline configuration that we had used in other papers 
\cite{jj-ppsn98anonymous} included
{\em overlaps} or volunteers running islands that had actually started in
a previous experiment instance in the set. In previous papers, we were
interested in measuring the number of users or their behavior in bulk
and this overlap was not so important, but
in this case our focus was on the evolutionary algorithm so we had to
make all volunteers in it started more or less at the same time and
from a random population. In fact, we managed to do so, except in some
byzantine cases, by making the clients restart when the cache size
collapses to 1 or to a size much smaller than the current; we called
this client configuration {\tt reboot} and {\tt cachecrash}.  This
configuration achieves a positive secondary effect: all clients
contribute to fill the cache, having thus an actual effect on the
chromosome pool and effectively making all clients present contribute
to the simulation.
